\chapter{Getting Started}

\emph{ML: this chapter is for you to rewrite once you get it all figured out.}

\section{Obtaining Ames Stereo Pipeline}

There are two ways to get the Ames Stereo Pipeline, you can either
download the source code and build it yourself, or you can download
prebuilt binaries for your system.  Building the code from source can
be quite an undertaking, and we recommend it only for the most
advanced users.  Most users will want to download and install the
binary distribution.

You can find the Ames Stereo Pipeline at \emph{URL?}

\section{Software Dependencies}

\subsection{The NASA Vision Workbench}

\emph{MJB: of course, don't forget to mention the SP's explicit dependence on the VW.}

\subsection{USGS Intergrated Software for Imagers and Spectrometers}

The Ames Stereo Pipeline depends on the Integrated Software for Imagers and Spectrometers (ISIS), version 3.1.17, availalbe from the USGS (http://isis.astrogeology.usgs.gov).  

\section{Building Ames Stereo Pipeline}

The horror!

List Dependecies ...

\section{Prebuilt Binaries}

The prebuilt binary route is not completely plug and play.  The
Ames Stereo Pipeline is built against the Integrated Software for
Imagers and Spectrometers (ISIS) suite, and you'll have to have
that installed on your system already.

When you download and unpack the prebuilt binary, called the
\texttt{isis\_stereovision} package (so named because it is a binary
build of the NASA Vision Workbench and the Ames Stereo Pipeline
built against ISIS), you will have a directory called
\texttt{isis\_stereovision/} which you can place anywhere on your
system.

The remainder of the setup is very, very similar to how ISIS itself
is set up.

First define an \texttt{ISIS\_STEREOVISION} environment variable like so:
\begin{verbatim}
 csh: setenv ISIS\_STEREOVISION /path/to/isis\_stereovision
bash: set ISIS\_STEREOVISION=/path/to/isis\_stereovision
\end{verbatim}

Then, source the appropriate \texttt{isis\_stereovisionStart} script:
\begin{verbatim}
 csh: source isis\_stereovisionStart.csh
bash: . isis\_stereovisionStart.sh
\end{verbatim}

\subsection*{Usage}

Some of the provided programs do not require the ISIS environment
to be set up, others do.  If you run into a problem like:
\begin{verbatim}
    dyld: Library not loaded: \$ISISROOT/lib/libisis3.dylib
      Referenced from: /path/to/isis\_stereovision/isis\_stereovision/bin/program
      Reason: image not found
    Trace/BPT trap
\end{verbatim}

You just need to set up your ISIS environment.

