\chapter{Frame Camera Models}

Ames Stereo Pipeline supports a generic Pinhole camera model with
several lens distortion models which cover common calibration
methods, and also the somewhat more complicated panoramic camera model.

\section{Pinhole Models}
\label{pinholemodels}

\section{Overview}

The generic pinhole model uses the following parameters:

\begin{itemize}{}
\item  \textit{fu} = The focal length in horizontal pixel units.
\item  \textit{fv} = The focal length in vertical pixel units.
\item  \textit{cu} = The horizontal offset of the principal 
point of the camera in the image plane in pixel units, from 0,0.
\item  \textit{cv} = The vertical offset of the principal 
point of the camera in the image plane in pixel units, from 0,0.
\item  \textit{pitch} = The size of each pixel in the units used to specify
the four parameters listed above.  This will usually either be 1.0 if they
are specified in pixel units or alternately the size of a pixel in millimeters.
\end{itemize}

The focal length is sometimes known as the \textit{principal
distance}. The value $cu$ is computed as half the image width in
pixels times the pitch, while $cv$ is half the image height in pixels
time the pitch.

A few sample pinhole models are shown later in the text.

Along with the basic pinhole camera parameters, a lens distortion model
can be added.  Note that the units used in the distortion model must
match the units used for the parameters listed above.  For example, if the
camera calibration was performed using units of millimeters the focal lengths etc. must be given in
units of millimeters and the pitch must be equal to the size of each pixel in millimeters.
The following lens distortion models are currently supported:

\begin{itemize}{}
\item  \textbf{Null} = A placeholder model that applies no distortion.

\item  \textbf{Tsai} = A common distortion model similar to the one used by OpenCV and THEIA.
 This model uses the following parameters:
  \begin{description}
    \item \textit{K1, K2} = Radial distortion parameters.
    \item \textit{P1, P2} = Tangential distortion parameters.
  \end{description}
\hfill \\ The following equations describe the distortion, starting with the undistorted pixel $(Px, Py)$:

\[ (x, y) = \left(\frac{Px - cu}{fu}, \frac{Py-cv}{fv}\right) \]
\[ r^{2} = x^{2} + y^{2} \]
\[ x(distorted) = x\left(K_{1}r^{2} + K_{2}r^{4} + 2P_{1}y + P_{2}\left(\frac{r^{2}}{x} + 2x\right)\right)  \]
\[ y(distorted) = y\left(K_{1}r^{2} + K_{2}r^{4} + 2P_{2}x + P_{1}\left(\frac{r^{2}}{y} + 2y\right)\right)  \]
\hfill \\ References:
\begin{description}
   \item Roger Tsai, A Versatile Camera Calibration Technique for a High-Accuracy 3D
          Machine Vision Metrology Using Off-the-shelf TV Cameras and Lenses
\end{description}
\hfill \\ Note that this model uses normalized pixel units.

\item  \textbf{Adjustable Tsai} = A variant of the Tsai model where any number of \textit{K} terms and a skew term (alpha) can be used.  Can apply the AgiSoft Lens calibration parameters.

\item  \textbf{Brown-Conrady} = An older model based on a centering angle.

 This model uses the following parameters:
  \begin{description}
    \item \textit{K1, K2, K3} = Radial distortion parameters.
    \item \textit{P1, P2} = Tangential distortion parameters.
    \item \textit{xp, yp} = Principal point offset.
    \item \textit{phi} = Tangential distortion angle in radians.
  \end{description}
\hfill \\ The following equations describe the distortion:
\[ x = x(distorted) - xp \]
\[ y = y(distorted) - yp \]
\[ r^{2} = x^{2} + y^{2} \]
\[ dr = K_{1}r^{3} + K_{2}r^{5} + K_{3}r^{7} \]
\[ x(undistorted) = x + x\frac{dr}{r} - (P_{1}r^{2} +P_{2}r^{4})\sin(phi) \]
\[ y(undistorted) = y + y\frac{dr}{r} + (P_{1}r^{2} +P_{2}r^{4})\cos(phi) \]
\hfill \\ Note that this model uses non-normalized pixel units, so they
are in mm.


\hfill \\ References:
\begin{description}
   \item Decentering Distortion of Lenses - D.C. Brown, 
          Photometric Engineering, pages 444-462, Vol. 32, No. 3, 1966
   \item Close-Range Camera Calibration - D.C. Brown, 
          Photogrammetric Engineering, pages 855-866, Vol. 37, No. 8, 1971
\end{description}

\item  \textbf{Photometrix} = A model matching the conventions used by the Australis software from Photometrix.

  \begin{description}
    \item \textit{K1, K2, K3} = Radial distortion parameters.
    \item \textit{P1, P2} = Tangential distortion parameters.
    \item \textit{xp, yp} = Principal point offset.
    \item \textit{B1, B2} = Unused parameters.
  \end{description}
\hfill \\ The following equations describe the distortion:
\[ x = x(distorted) - xp \]
\[ y = y(distorted) - yp \]
\[ r^{2} = x^{2} + y^{2} \]
\[ dr = K_{1}r^{3} + K_{2}r^{5} + K_{3}r^{7} \]
\[ x(undistorted) = x + x\frac{dr}{r} + P_{1}(r^{2} +2x^{2}) + 2P_{2}xy \]
\[ y(undistorted) = y + y\frac{dr}{r} + P_{2}(r^{2} +2y^{2}) + 2P_{1}xy \]
\hfill \\ Note that this model uses non-normalized pixel units, so they
are in mm.

\item  \textbf{RPC} = A rational polynomial coefficient model.

In this model, one goes from distorted coordinates $(x, y)$ to undistorted
coordinates via the formula

\[ x(undistorted) = \frac{P_1(x, y)}{Q_1(x, y)} \]
\[ y(undistorted) = \frac{P_2(x, y)}{Q_2(x, y)} \]

The functions in the numerator and denominator are polynomials in $x$
and $y$ with certain coefficients. The degree of
polynomials can be any positive integer.

RPC distortion models can be generated as approximations to other pre-existing
models with the tool \texttt{convert\_pinhole\_model} (section \ref{convertpinholemodel}).

This tool also creates RPC to speed up the reverse operation, of going
from undistorted to distorted pixels, and those polynomial coefficients
are also saved as part of the model.

\end{itemize}

\hrule
\subsection{File Formats}
\label{file_format}
\bigskip

ASP pinhole model files are written in an easy to work with plain text format 
using the extension \texttt{.tsai}.
A sample file is shown below. 

\begin{verbatim}
VERSION_4
PINHOLE
fu = 28.429
fv = 28.429
cu = 17.9712
cv = 11.9808
u_direction = 1  0  0
v_direction = 0  1  0
w_direction = 0  0  1
C = 266.943 -105.583 -2.14189
R = 0.0825447 0.996303 -0.0238243 -0.996008 0.0832884 0.0321213 0.0339869 0.0210777 0.9992
pitch = 0.0064
Photometrix
xp = 0.004
yp = -0.191
k1 = 1.31024e-04
k2 = -2.05354e-07
k3 = -5.28558e-011
p1 = 7.2359e-006
p2 = 2.2656e-006
b1 = 0.0
b2 = 0.0
\end{verbatim}

The first half of the file is the same for all pinhole models:

\begin{itemize}{}
\item  \texttt{VERSION\_X} = A header line used to track the format of the file.
\item  \texttt{PINHOLE} = The type of camera model, so that other types can be stored with the .tsai extension.
\item  \texttt{fu, fv, cu, cv} = The first four intrinsic parameters described in the previous section.
\item  \texttt{u, v, and w\_direction} = These lines allow an additional permutation of the 
axes of the camera coordinates.  By default, the positive column direction aligns with x, the
positive row direction aligns with y, and downward into the image aligns with z.
\item  \texttt{C} = The location of the camera center, usually in the geocentric coordinate system (GCC/ECEF).
\item  \texttt{R} = The rotation matrix describing the camera's absolute pose in the coordinate system.
\item  \texttt{pitch} = The pitch intrinsic parameter described in the previous section.
\end{itemize}

The second half of the file describes the lens distortion model being used.  The name of the
distortion model appears first, followed by a list of the parameters for that model.  The number
of parameters may be different for each distortion type.  Samples of each format are shown below:

\begin{itemize}{}
\item  \textbf{Null}
\begin{verbatim}
NULL
\end{verbatim}

\item  \textbf{Tsai}
\begin{verbatim}
TSAI
k1 = 1.31024e-04
k2 = -2.05354e-07
p1 = 0.5
p2 = 0.4
\end{verbatim}

\item  \textbf{Adjustable Tsai}
\begin{verbatim}
AdjustableTSAI
Radial Coeff: Vector3(1.31024e-04, 1.31024e-07, 1.31024e-08)
Tangential Coeff: Vector2(-2.05354e-07, 1.05354e-07)
Alpha: 0.4
\end{verbatim}

\item  \textbf{Brown-Conrady}
\begin{verbatim}
BrownConrady
xp = 0.5
yp = 0.4
k1 = 1.31024e-04
k2 = -2.05354e-07
k3 = 1.31024e-08
p1 = 0.5
p2 = 0.4
phi = 0.001
\end{verbatim}

\item  \textbf{Photometrix}
\begin{verbatim}
Photometrix
xp = 0.004
yp = -0.191
k1 = 1.31024e-04
k2 = -2.05354e-07
k3 = -5.28558e-011
p1 = 7.2359e-006
p2 = 2.2656e-006
b1 = 0.0
b2 = 0.0
\end{verbatim}

\item  \textbf{RPC}

\begin{verbatim}
RPC
rpc_degree = 1
image_size = 5760 3840
distortion_num_x   = 0 1 0
distortion_den_x   = 1 0 0
distortion_num_y   = 0 0 1
distortion_den_y   = 1 0 0
undistortion_num_x = 0 1 0
undistortion_den_x = 1 0 0
undistortion_num_y = 0 0 1
undistortion_den_y = 1 0 0
\end{verbatim}

This sample RPC lens distortion model represents the case of no distortion, 
when the degree of the polynomials is 1, and both the distortion and undistortion 
formula leave the pixels unchanged, that is, the distortion transform is
\begin{equation*}
(x, y) \to (x, y) = \left(\frac{ 0 + 1\cdot x + 0\cdot y}{1 + 0\cdot x + 0\cdot y},
 \frac{0 + 0\cdot x + 1\cdot y)}{1 + 0\cdot x + 0\cdot y}\right).
\end{equation*}

In general, if the degree of the polynomials is $n$, there are $2(n+1)(n+2)$ coefficients. 
The zero-th degree coefficients in the denominator are always set to 1.

\end{itemize}{}

For several years Ames Stereo Pipeline generated pinhole files in the binary \texttt{.pinhole} format.
That format is no longer supported.

Also in the past Ames Stereo Pipeline has generated a shorter version of the current file
format, also with the extension \texttt{.tsai}, which only supported the TSAI lens distortion model.
Existing files in that format can still be used by ASP.

Note that the \texttt{orbitviz} tool can be useful for checking the formatting of \texttt{.tsai}
files you create and to estimate the position and orientation. To inspect the orientation use 
the optional \texttt{.dae} model file input option and observe the rotation of the 3D model.

\section{Panoramic Camera Model}
\label{panoramic}

ASP also supports a simple panoramic/optical bar camera model for use with images such as
the declassified Corona KH4 and Keyhole KH9 images. It implements the model
from \cite{schenk2003rigorous} with the motion compensation from \cite{sohn2004mathematical}.

Such a model looks as follows:
\begin{verbatim}
VERSION_4
OPTICAL_BAR
image_size = 110507 7904
image_center = 55253.5 3952
pitch = 7.0e-06
f = 0.61000001430511475
scan_angle = 1.22173
scan_rate = 3.3500000000000001
forward_tilt = -0.261799
iC = -1047140.9611702315 5508464.4323527571 3340425.4078937685
iR = -0.96635634448923746 -0.16918164442572045 0.1937343197650008 -0.23427205529446918 0.26804084264169648 -0.93448954557235941 0.10616976770014927 -0.94843643849513648 -0.29865750042675621
speed = 7700
mean_earth_radius = 6371000
mean_surface_elevation = 4000
use_motion_compensation = 1.0
scan_dir = left
\end{verbatim}

Here, the image size and center are given in pixels, with the width followed by the
height. The pixel pitch and focal length \texttt{f} are in meters. The
scan angle is in radians (in this example it is 70$^\circ$), the scan
rate is in radians per second, the forward tilt is in radians,
the speed is in meters per second, and the Earth radius and mean
surface elevation are in meters. The initial camera center \texttt{iC} is 
in meters, and the rotation matrix \texttt{iR} stores the absolute pose.
\texttt{scan\_dir} must be set to 'left' or 'right'.
\texttt{scan\_dir} and \texttt{use\_motion\_compensation}
control how the sensor model accounts accounts for the motion of the satellite
during the image scan.  Without the benefit of detailed historical documents it may
require experimentation to find the good initial values for these cameras.  When using
\texttt{bundle\_adjust}, the only intrinsic parameters that are solved for are 
\texttt{speed} and \texttt{use\_motion\_compensation}.
