\chapter{Introduction}

The NASA Ames StereoPipeline is a suite of automated geodesy and
stereogrammetry tools designed for processing planetary imagery
captured from orbiting and landed robotic explorers on other planets.
It was designed to process stereo imagery captured by NASA
spacecraft and produce cartographic products including DEM,
ortho-projected imagery, and 3D models.  These data products are
suitable for science analysis, mission planning, and public outreach.

\section{Photometry Toolkit}
Yes, this software is still in developement.

\section{Warnings to users of the Ames Stereo Pipeline ALPHA}

This is an {\bf ALPHA} release of the Stereo Pipeline.  There are many
known bugs and incomplete features. The API and command line options
will almost certainly change prior to the final release.  Some of the
documentation is incomplete and some of it may be out of date or
incorrect.  Although we hope you will find this release helpful, you
use it at your own risk.

While we are confident that the algorithms used by this software are
robust, they have not been systematically tested or rigorously
compared to other methods in the peer-reviewed literature. We have a
number of efforts underway to carefully compare Stereo
Pipeline-generated data products to those produced using established
processes, and we will publish those results as they become available.
In the meantime, {\bf we strongly recommend that you consult us first
  before publishing any results based on the cartographic products
  produced by this software}. You have been warned!

